Flowchart of Current Algorithm

### 2009-02-05 docs/flowchart/flowchart.tex
removed div_etarho from code.  notes are still a work in progress to describe the change

\item After {\bf React State}, we set $(\rho h)_0 = {\rm{\bf Avg}}(\rho h)$ in 
plane-parallel and $(\rho h)_0 = (\rho h)_0 - {\rm{\bf Avg}}[(\rho h)_0 - (\rho h)]$ 
in spherical.  This means that {\bf React Base} no longer exists, and the intermediate states, 
$(\rho h)_0^{(1)}$ and $(\rho h)_0^{(2)}$, no longer have to exist.  
{\bf Advect Base Enthalpy} will advance $(\rho h)_0^n \rightarrow (\rho h)_0^{n+1}$ 
directly.  This also means we don't have to deal with $\eta_{\rho h}$ or a 
{\bf Diffuse Base}.

@@

\item Should we replace {\bf Correct Base} with $\rho_0 = {\rm{\bf Avg}}(\rho)$ in 
plane-parallel and $\rho_0 = \rho_0 - {\rm{\bf Avg}}(\rho_0 - \rho)$ in spherical?
This eliminates the need for $\nabla\cdot\etarho$.

\item Should we eliminate {\bf Advect Base Pressure} entirely, and instead directly
enforce HSE after {\bf Correct Base}?  {\bf Advect Base Pressure} was just a fancy
way of enforcing HSE anyway, so why not just compute the new pressure directly?

@@

\item {\bf Correct Base}$[\rho_0^{\inp}, (\nabla\cdot\etarho\er)^{\inp}] \rightarrow [\rho_0^{\outp}]$\\
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$.  For both plane-parallel and spherical
we use
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \dt (\nabla\cdot\etarho\er)^{\inp}_j \enskip . 
\end{equation}

@@

\item[spherical:] Set $(\rho h)_0^{n} = (\rho h)_0^{n} - {\rm{\bf Avg}}\left[(\rho h)_0^{n} - (\rho h)^{(1)}\right]$.

>>>>

\item After {\bf React State}, we set $(\rho h)_0 = {\rm{\bf Avg}}(\rho h)$ in 
plane-parallel and $(\rho h)_0 = (\rho h)_0 + {\rm{\bf Avg}}[(\rho h) - (\rho h)_0]$ 
in spherical.  This means that {\bf React Base} no longer exists, and the intermediate states, 
$(\rho h)_0^{(1)}$ and $(\rho h)_0^{(2)}$, no longer have to exist.  
{\bf Advect Base Enthalpy} will advance $(\rho h)_0^n \rightarrow (\rho h)_0^{n+1}$ 
directly.  This also means we don't have to deal with $\eta_{\rho h}$ or a 
{\bf Diffuse Base}.

\item We replaced {\bf Correct Base} with $\rho_0 = {\rm{\bf Avg}}(\rho)$ in 
plane-parallel and $\rho_0 = \rho_0 + {\rm{\bf Avg}}(\rho - \rho_0)$ in spherical,
eliminating the need for $\nabla\cdot\etarho$.

@@

\begin{itemize}
\item Should we eliminate {\bf Advect Base Pressure} entirely, and instead directly
enforce HSE after {\bf Correct Base}?  {\bf Advect Base Pressure} was just a fancy
way of enforcing HSE anyway, so why not just compute the new pressure directly?

@@

\item {\bf Correct Base}$[\rho_0^{\inp}, \rho^{\inp}] \rightarrow [\rho_0^{\outp}]$\\
is the process by which we adjust the base state density to account for
large-scale mixing.  It can also be used to adjust the base state enthalpy
to account for large-scale mixing, reactions, and thermal diffusion.

\begin{description}
\item[plane-parallel:] Set $\rho_0^{\outp} = {\bf Avg}(\rho^{\inp})$.
\item[spherical:] Set $\rho_0^{\outp} = \rho_0^{\inp} + {\bf Avg}(\rho^{\inp} - \rho_0^{\inp})$.
\end{description}

@@

\item[spherical:] Set $(\rho h)_0^{n} = (\rho h)_0^{n} + {\rm{\bf Avg}}\left[(\rho h)^{(1)} - (\rho h)_0^{n}\right]$.
